Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Ideally, since the literature suggests that self-confidence depends partly on one's integration within social networks [@OECD2009], we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too :

@@

The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this. But we still think that should be included in a future research on that topic.

>>>>

Ideally, since the literature suggests that self-confidence depends partly on one's integration within social networks [@OECD2009], we should be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too :

@@

The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this for the time being. But we still think that should be included in a future research on that topic.
